\chapter{Introduction}
\label{introduction}

{\bf MRB says: I would think of these first three 
sections as close to just a single section. I might 
also suggest the opening section be "Questions in 
galaxy evolution." You could have a paragraph or two
on the thumbnail history --- Herschel to Slipher and
Hubble to modern day. Then give the theoretical context.
Fluctuations grow, halos collapse, baryons radiate their
energy are collapse in the center, form disks, and those
disks form stars. Stellar and AGN processes may feedback.
Then the questions: what ends star formation at high mass?
what  regulates it at low mass? how are 
stellar mass and DM mass related? Then finally mention
simulations that exist that compare the two, if reliable
observations can be made to compare to.
}

\section{The Study of Galaxies}

\section{Introduction to Survey Astronomy}

\section{Questions in Galaxy Evolution}

\section{Star Formation in Galaxies}

{\bf MRB says: I assume this section is about observations 
of SF in galaxies. That would make sense. You need to 
introduce importance of dust here.}

{\bf MRB says: You probably want to also have something
about observation of stellar mass distribution.}

\subsection{What can we infer from Photometry?}

{\bf MRB: Maybe combine this with the next.}

\subsection{What can we infer from a Galaxy Spectrum?}

\section{Star Formation in the Local Universe: NASA Sloan Atlas and MaNGA}

{\bf MRB: Maybe Legacy, plus MaNGA. NSA can be mentioned
as a reanalysis of Legacy photometry}


