% the acknowledgments section

\newthought{This thesis owes its existence} to many people, either directly or indirectly, and it is a pleasure to finally acknowledge and thank those who have been a part of this incredible journey. I would like to express my gratitude to my advisor, Prof. Michael Blanton, for being a mentor, guide, manager and teacher all at once and for supporting me at every step of this process since I began working with him six years ago. Mike has been an inspiration to me, not just as a scientist and a teacher, but also in the gracious, patient and just manner in which he carries out every aspect of his life. I would like to thank Prof. David Hogg for being unfailingly encouraging of all my endeavors and for his infectious enthusiasm for pretty much anything related to the sciences. Teaching Observational Astronomy with David was definitely one of the highlights of my grad school life at NYU. I would like to thank my thesis committee members, Prof. Jeremy Tinker, Prof. Anthony Pullen and Prof. David Grier for having been supportive through the entire process and giving me invaluable feedback on the substance of this thesis.\\

My friends in the Physics department at NYU have been a source of immense support throughout the years. I would like to thank: Chang, Geoff and MJ, for all the banter, astronomy and otherwise; the 639B crew that chose the CSMR way of life, Cato, Christine and Ruben, for always having wonderful counsel to offer on any subject matter; Mark and Melissa, for all the data science adventures; and last but not the least, the members of the original \#DreamTeam, Doycho and Kilian, for sticking it out with me until the very end.\\

I would like to acknowledge my friends outside of grad school: Anu, Aparajita, Archana, Harsh, Ken, Manas, Monika, Neha, Sauby and Shikha, for being my family away from family and my support system; my roommates, Maddie and Marie, for creating a wonderful home environment for me; Adrien, Joy, Joyce, Lidya, Marie and Marion, for all the New York adventures.\\

My journey in Physics owes its existence to my brilliant parents, M.D. Srinivas and R. Vijayalakshmi. As students of science themselves, they have taught me by example the joys of a life in the pursuit of academic excellence and intellectual satisfaction. Their constant and unconditional love and support for me has helped me immensely in seeing this dream to fruition. To my sister, Prabha, who has always been and continues to be my hero, this thesis would have been impossible without you, Krishna and Srikar cheering me on to the finish line.\\

Finally, to anyone who may be despairing at seeing a creative enterprise to its conclusion and all those who are wearily engaged in fighting the good fight to fulfill your dreams, I would like to refer you to something I held on to - the simple yet powerful words of the protagonist of the iconic 2019 Hindi movie, Gully Boy: \emph{``Apna time aayega."}\\
